---
title: "Systematic survey report"
author: "Madalina Olteanu, Fabrice Rossi & Florian Yger"
date: "January 2023"
output: html_document
---

```{css, echo=FALSE}
span.C1 {
  color: grey;
}
span.C2 {
  color: grey;
}
span.C3 {
  color: #d7301f;
  text-decoration-line: underline;
}
span.C4 {
  color: #fdcc8a;
}
span.C5 {
  color: #fc8d59;
}
span.C6 {
  font-weight: bold;
  color: #d7301f;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r}
library(readr)
library(dplyr)
library(stringr)
```

```{r}
s2qdir <- "s2q"
s2_curated_papers <- read_csv(file.path(s2qdir, "s2_papers_curated.csv"))
s2_curated_papers <-
  s2_curated_papers |>
  distinct(id, .keep_all = TRUE) |>
  arrange(title)
gsqdir <- "gsq"
gs_curated_papers <-
  read_csv(file.path(gsqdir, "gs_papers_curated.csv"),
    col_types = cols(
      id = col_character(),
      title = col_character(),
      query = col_character(),
      s2_id = col_character()
    )
  )
```

```{r}
paper_stats <- tibble(
  Site = c("Semantic Scholar", "Google Scholar"),
  Answers = c(400, 400),
  `Unique papers` = c(nrow(s2_curated_papers), nrow(gs_curated_papers))
)
gs_in_s2 <-
  gs_curated_papers |>
  filter(!is.na(s2_id))
gs_dup_s2 <- gs_in_s2 |>
  nrow() - gs_in_s2 |>
  distinct(s2_id) |>
  nrow()
gs_in_s2 <-
  gs_in_s2 |> distinct(s2_id, .keep_all = TRUE)
s2_dup <- s2_curated_papers |>
  filter(!is.na(duplicated)) |>
  nrow()
paper_stats$Duplicated <- c(s2_dup, gs_dup_s2)
```

```{r}
s2_only <- s2_curated_papers |> anti_join(gs_curated_papers, by = c(id = "s2_id"))
gs_only <- gs_curated_papers |>
  filter(is.na(s2_id)) |>
  select(-s2_id)
both <- s2_curated_papers |> semi_join(gs_curated_papers, by = c(id = "s2_id"))
paper_stats$Specific <- c(nrow(s2_only), nrow(gs_only))
```

```{r}
survey_results <- read_csv("survey_results.csv", col_types = cols(
  index = col_integer(),
  class = col_integer(),
  title = col_character(),
  type = col_character(),
  language = col_character(),
  set = col_character(),
  s2_id = col_character(),
  gs_id = col_character(),
  alternate_gs_id = col_character(),
  alternate_s2_id = col_character(),
  original_article = col_character()
))
```

## Initial queries
### Aggregated statistics 
We collected the first 100 answers to the four queries on both [Google Scholar (GS)](https://scholar.google.com) 
and [Semantic Scholar (S2)](https://www.semanticscholar.org/). As shown in the 
following table, answers from GS are less variable than those from S2. GS has only 
one undetected duplicate, which corresponds to two versions of the Chandola et al. 
survey. 

```{r}
knitr::kable(paper_stats)
```
The two sets of answers have `r gs_in_s2 |> nrow()` papers in common which could be
seen as surprisingly low. Combined, the queries identified `r survey_results |> nrow()` documents.

### Result quality
```{r}
not_english <- survey_results |> filter(language!="English") |> nrow()
not_paper <- survey_results |> filter(type %in% c("master thesis", "plagiarism", "student", "non existent")) |> nrow()
preprint <- survey_results |> filter(type =="preprint") |> nrow()
```

In addition to the duplicated papers, a few of the results have been excluded from 
the subsequent analysis because of various issues:

- `r not_english` papers were not written in English
- `r not_paper` documents were excluded for various issues: a blatant case of plagiarism, 
  a master thesis, a paper from a student workshop and papers that were impossible
  to track on any publication platform (2 papers)
- `r preprint`  documents were preprints available only on Arxiv

Note also that `r survey_results |> filter(is.na(s2_id)) |> nrow()` papers found on 
GS were not indexed by S2.


```{r}
survey_results <- survey_results |> mutate(on_topic = class >= 4)
on_topic_papers <- survey_results |> filter(on_topic)
on_topic_counts <- survey_results |> filter(class !=1) |> group_by(set, on_topic) |> summarise(N=n())
on_topic_rates <- on_topic_counts |> 
  mutate(freq=100*N/sum(N)) |> 
  filter(on_topic) |> 
  select(Set=set, `On topic %`=freq)
```

We read the titles and abstracts of the remaining `r survey_results |> filter(class !=1) |> nrow()` 
papers to selected the ones that were actually about outlier and anomaly detection, finding 
a total of `r nrow(on_topic_papers)` papers.

Notice that, as expected, the precision of the queries depend on the set, as 
shown on the following table:
```{r}
knitr::kable(on_topic_rates)
```

Notice that while the common papers between GS and SS are much more likely to
be on topic, we would have miss a lot of potential candidates by focusing only
on one of the two search engines, as shown by the row counts of papers:
```{r}
knitr::kable(on_topic_counts |> filter(on_topic) |> select(Set = set, `Papers on topic` = N))
```

### Paper selection 
Finally based on titles, abstracts and on reading the papers when needed, we
identified a total of `r survey_results |> filter(class==6) |> nrow()` general
survey paper. The breakdown of the papers between sources is given below and justify 
again using both search engines:
```{r}
knitr::kable(survey_results |> filter(class==6) |> count(set)|> select(Set = set, `General survey` = n))
```

We also identified a large collection of `r survey_results |> filter(class==5) |> nrow()` 
papers that surveyed some specific aspects of outlier/anomaly detection but they
were not general enough to be considered in the meta-survey. The breakdown by source 
is the following one:
```{r}
knitr::kable(survey_results |> filter(class==5) |> count(set)|> select(Set = set, `Specific survey` = n))
```


## Paper list
```{r}
class_name <- c("Excluded", "Not on outliers", "Text book or tutorial", "Not a survey", "Not a general survey", "General survey")
counts <- bind_cols(tibble(type=class_name), survey_results |> count(class) |> mutate(class=str_c("C", class), n))
knitr::kable(counts)
```

### Color codes
```{=html}
<ul>
  <li>C6 : <span class="C6">General survey papers about outlier detection (selected)</span></li>
  <li>C5 : <span class="C5">Survey papers about specific aspects of outlier detection</span></li>
  <li>C4 : <span class="C4">about outlier/anomaly but not surveys</span></li>
  <li>C3 : <span class="C3">monographs, text books, chapters or tutorial about outlier detection</span></li>
  <li>C2 : <span class="C2">not about outlier/anomaly </span></li>
  <li>C1 : <span class="C1">excluded papers</span></li>
</ul>  
```

### Full list
```{r, results='asis'}
cat("<ul>\n")
#for (i in 1:5) {
for (i in 1:nrow(survey_results)) {
  paper_class <- paste0("C", survey_results$class[i])
  cat("<li>", survey_results$index[i], " ", paper_class, "\n", sep="")
  if (!is.na(survey_results$s2_id[i])) {
    cat("<a href=\"https://www.semanticscholar.org/paper/", survey_results$s2_id[i], "\">", sep = "")
  } else if (!is.na(survey_results$gs_id[i])) {
    cat("<a href=\"https://scholar.google.com/scholar?cluster=", survey_results$gs_id[i], "&hl=en\">", sep = "")
  }
  cat("<span class=\"", paper_class, "\">", survey_results$title[i], "</span>", sep = "")
  if (!is.na(survey_results$s2_id[i])) {
    cat(" (on S2)</a>")
  } else if (!is.na(survey_results$gs_id[i])) {
    cat(" (on GS)</a>")
  }
  cat("</li>\n")
}
cat("</ul>\n")
```
